Selecting and ranking interesting pairs of cyclic temporal granularities

### 2021-01-13 paper/main.Rmd
including some figures

We are interested in assessing structure in probability distributions of the measured variable across bivariate cyclic granularities. We propose a measure called Median Maximum Pairwise Distances (MMPD) to evaluate structure in such a design.

@@

With reference to the graphical design in \ref{@Gupta2020-vo}, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of the facet variables. Thus the metric could be obtained by computing maximum pairwise distances between distributions of the continuous random variable across x-axis categories for all facets and then taking the median of those maximum pairwise distances across facets. This would help capture the average maximum difference in distribution of the measurement variable explained by the two cyclic granularities together. We call this metric MMPD which stands for Median Maximum Pairwise Distances. In the next section we shall see how we go about computing this measure.

@@

@@

```{r, eval = FALSE}
knitr::include_graphics(here::here("simulations/null_design/figs/normalised","gamma_ridge_nxbynfacet.png"))
```

>>>>

We are interested in assessing structure in probability distributions of the measured variable across bivariate cyclic granularities. We propose a measure called Median Maximum Pairwise Distances (wpd) to evaluate structure in such a design.

@@

With reference to the graphical design in \ref{@Gupta2020-vo}, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of the facet variables. Thus the metric could be obtained by computing maximum pairwise distances between distributions of the continuous random variable across x-axis categories for all facets and then taking the median of those maximum pairwise distances across facets. This would help capture the average maximum difference in distribution of the measurement variable explained by the two cyclic granularities together. We call this metric wpd which stands for Median Maximum Pairwise Distances. In the next section we shall see how we go about computing this measure.

@@

```{r all-design-relative, fig.cap = "Distribution of wpd under different designs are overlapped to see how they measure relative to each other. We would have expected values of wpd to be such that vary_facet is less than vary_x is less than vary_all but distribution of vary_x to lie above vary_facet."}

library(readr)
library(tidyverse)

vary_x <- read_rds("simulations/vary_x/null_design_quantrans/data-agg/all_data_wpd_N01.rds")

vary_all <- read_rds("simulations/vary_all/raw/data-agg/all_data_wpd_N01.rds")

vary_facet <- read_rds("simulations/vary_facet/raw/data-agg/all_data_wpd_N01.rds")

all_design <- bind_rows(vary_facet, vary_x, vary_all, .id = "design") %>% 
  mutate(design = case_when(
    design=="1" ~ "vary_facet",
    design=="2" ~ "vary_x",
    design=="3" ~ "vary_all",
    TRUE ~ as.character(design)                                                                 ))

all_design %>% 
  ggplot() +
  geom_histogram(aes(x=value, fill = design), 
                 alpha = 0.7) +
  scale_fill_brewer(palette = "Dark2")  +
  facet_wrap(~w, labeller = "label_both")
```

@@

```{r normal01-norm, fig.cap="Density plots of normalised wpd is shown for Normal(0,1) distribution. The mean and sd of the distribution looks almost similar for different facet and x-axis categories.", fig.pos="h"}

knitr::include_graphics(here::here("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_N01.png"))
```
